### 2023-11-17 main.tex
^^

	\Omega=\bigotimes_{x=1}^{L}\Omega_{x}\qquad \Omega_{x}=\left\{|\tau_{x}\rangle\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}

@@

This notation is equivalent to the one introduced. Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$. Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$. With this notation, we have that 
\begin{equation}\label{notation}
	|n^{x}\rangle =|\tau_{x}\rangle \qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
\end{equation}
with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$.
\end{comment} 
The ground state of the Hamiltonian $H^{''}$ is given by 
\begin{equation}\label{ResulsBasis}
	|\Psi^{''} \rangle= \sum_{\bm{\tau}\in \Omega}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} (\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\bm{\tau}\rangle
\end{equation}
%\begin{equation}\label{ResulsBasis}
%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
%\end{equation}
where 
\begin{equation}
    \delta_{\tau_{x},N}:=\begin{cases}
        N\quad \text{if}\quad \tau_{x}=N\\
        0\quad \text{otherwise}
    \end{cases}
\end{equation}

@@

	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega}\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}

@@

such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. \\

@@

	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt

@@

    |\Psi^{'}\rangle =\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 

@@

 By considering a fixed $\bm{\tau}\in \Omega$, and by using \eqref{goodTP-S2} by using the explici formula for $|\Psi^{''}\rangle$ we obtain 

@@

		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau},\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+

@@

	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})

@@

	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle

@@

	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
	=&\sum_{\bm{\tau}\in \Omega}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle

@@

		|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
	where, for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})\in \Omega$,

@@

				|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle

@@

				\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_x,i_{x}}\right)\nonumber\\
				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\

@@

			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega$, then we have 
					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
					%=&\sum_{\bm{\sigma}\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle

@@

					\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=1

@@

				\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1

@@

				\Omega_{\ell}=\left\{\bm{\tau}\in \Omega\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}

@@

				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1

@@

				&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
			We now consider the second term of the above expression. For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ has $\ell<b$, then this term do not produce any contribution. On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$. Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species. By calling $r=\ell-b$ if $b\leq \ell$ we have that 
				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<i_{q_{b}\leq L}=1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
				=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\dt

@@

				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt

@@

				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt

@@

	|\Psi^{'}\rangle=\sum_{\bm{\tau}\in\Omega}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle

@@

	|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})|\bm{\tau}\rangle

@@

	\widehat{\Omega}^{m}=\left\{\bm{\tau}\in \Omega\;:\; \tau_{y_{1}}=s_{1},\ldots,\tau_{y_{m}}=s_{m}\right\}

@@

\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)

@@

&\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)= \sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi^{'}(\tau)\nonumber

@@

\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
We introduce an index $\ell\in \{0,\ldots, L-m\}$ that denotes the number of empty occupations in an arbitrary configuration $\bm{\tau}\in \widehat{\Omega}^{m}$, i.e. $\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$. We also introduce the space 
\widehat{\Omega}^{m}_{\ell}=\left\{\bm{\tau}\in \widehat{\Omega}^{m}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}

@@

&\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)= \sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)\nonumber

@@

\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)

>>>>

	\Omega^{'}=\bigotimes_{x=1}^{L}\Omega_{x}^{'}\qquad \Omega_{x}^{'}=\left\{|\tau_{x}\rangle\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}

@@

This notation is equivalent to the one introduced. Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$. Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$. With this notation, we have that 
\begin{equation}\label{notation}
	|n^{x}\rangle =|\tau_{x}\rangle \qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
\end{equation}
with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$.
\end{comment} 
The ground state of the Hamiltonian $H^{''}$ is given by 
\begin{equation}\label{ResulsBasis}
	|\Psi^{''} \rangle= \sum_{\bm{\tau}\in \Omega^{'}}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} (\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\bm{\tau}\rangle
\end{equation}
%\begin{equation}\label{ResulsBasis}
%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
%\end{equation}
where 
\begin{equation}
    \delta_{\tau_{x},N}:=\begin{cases}
        N\quad \text{if}\quad \tau_{x}=N\\
        0\quad \text{otherwise}
    \end{cases}
\end{equation}

@@

	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega^{'}}\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}

@@

such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}^{'}$. \\

@@

	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega^{'}}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt

@@

    |\Psi^{'}\rangle =\sum_{\bm{\tau}\in \Omega^{'}}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 

@@

 By considering a fixed $\bm{\tau}\in \Omega^{'}$, and by using \eqref{goodTP-S2} by using the explici formula for $|\Psi^{''}\rangle$ we obtain 

@@

		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau},\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+

@@

	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})

@@

	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle

@@

	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
	=&\sum_{\bm{\tau}\in \Omega^{'}}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle

@@

		|\Psi\rangle=\sum_{\bm{\tau}\in \Omega^{'}}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
	where, for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})\in \Omega^{'}$,

@@

				|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle

@@

				\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_x,i_{x}}\right)\nonumber\\
				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\

@@

			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
					%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle

@@

					\sum_{\bm{\tau}\in\Omega^{'}}\langle \bm{\tau}|\Psi\rangle=1

@@

				\sum_{\bm{\tau}\in \Omega^{'}}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega^{'}}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1

@@

				\Omega_{\ell}^{'}=\left\{\bm{\tau}\in \Omega^{'}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}

@@

				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})\nonumber
				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1

@@

				&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})\nonumber
				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
			We now consider the second term of the above expression. For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}^{'}$ has $\ell<b$, then this term do not produce any contribution. On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}^{'}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$. Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species. By calling $r=\ell-b$ if $b\leq \ell$ we have that 
				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<i_{q_{b}\leq L}=1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
				=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}^{'}}\Psi^{'}(\bm{\tau})\dt

@@

				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})=0\dt

@@

				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})=0\dt

@@

	|\Psi^{'}\rangle=\sum_{\bm{\tau}\in\Omega^{'}}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle

@@

	|\Psi\rangle=\sum_{\bm{\tau}\in \Omega^{'}}\Psi(\bm{\tau})|\bm{\tau}\rangle

@@

	\widehat{\Omega^{'}}^{m}=\left\{\bm{\tau}\in \Omeg^{'}a\;:\; \tau_{y_{1}}=s_{1},\ldots,\tau_{y_{m}}=s_{m}\right\}

@@

\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)

@@

&\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)= \sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi^{'}(\tau)\nonumber

@@

\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
We introduce an index $\ell\in \{0,\ldots, L-m\}$ that denotes the number of empty occupations in an arbitrary configuration $\bm{\tau}\in \widehat{\Omega^{'}}^{m}$, i.e. $\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$. We also introduce the space 
\widehat{\Omega^{'}}^{m}_{\ell}=\left\{\bm{\tau}\in \widehat{\Omega^{'}}^{m}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}

@@

&\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)= \sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\tau)\nonumber

@@

\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
